%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Đỗ Quốc Cường}{}{}{\contactline{}{\href{https://www.github.com/}{KazegamiKuon}}{\href{https://www.linkedin.com/}{kazegamikuon}}{\href{mailto:quoccuonguit.1998@gmail.com}{quoccuonguit.1998@gmail.com}}{\href{tel:+84354600297}{0354600297}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Aperia}
\descript{SOFTWARE DEVELOPER}
\location{Sep 2021 – Current}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item \textbf{Technical:} React, Redux, JavaScript, jQuery, Ajax, XHR, JSON, Jest, JSX syntax, Kendo, Telerik, Bootstrap,HTML, CSS, .Net core/framework, Entity Framework, CI/CD, Git,API/code library support for React, develop tools for BE and FE, etc.
\item \textbf{Job}: Work as a member of the Scrum team. Review, deploy and manage git source code. Join a meeting with BA, US Manager in order to support and discuss technical solutions that resolve security, performance issues and adapt requirements. Integrate with WPF applications, system configuration, or other teams.
\item \textbf{Project:} Financial Services (Fintech). Develop new features and old features using PCI knowledge and financial knowledge to analyze, improve, and resolve requirements.
\end{tightemize}
\sectionsep

\runsubsection{Vingroup Big Data Institute}
\descript{TECHNOLOGY SPECIALIST}
\location{Oct 2020 – Sep 2021}
\begin{tightemize}
\sectionsep
\item \textbf{Technical}: Python, Git, Bash, TensorFlow, PyTorch, Pandas, NumPy etc.
\item \textbf{Job}: Learn a great deal from AI Academy researchers in computer vision, machine learning, deep learning, and natural language processing. Research and develop AI models (such as DAE,GAN, RNN, etc.) to resolve massive sequence data problems. Create and modify various tools for analyzing and pre-processing sequence data.
\item  \textbf{Project:} Processing and predicting big sequence data that misses a lot of data.
\end{tightemize}
\sectionsep

\runsubsection{I3 Solution Australia}
\descript{FULL-STACK DEVELOPER}
\location{Jun 2018 – Oct 2020}
\begin{tightemize}
\sectionsep
\item \textbf{Technical}: React, Redux, Bootstrap, Material UI, JavaScript, jQuery ,HTML, CSS, SQL, DAX, ASP.Net, Entity Framework etc.
\item \textbf{Job}: Joining in build up react library of company. Design, manage, develop, tweak and optimize service, API, Data base, Front End and Back End. Design and develop a workflow for proposed solutions of each requirement. Design and manage database (Microsoft SQL)  as server-side.
\item {\textbf{Project:} Transportation management system - \textbf{Contribute}: FE 30\% - BE 100\% - DB 100\%}
\item {Studying and Researching about Data Warehouse, analysis service and business intelligence}
\item {\textbf{Project:} Booking services  web application - \textbf{Contribute}: FE 60\% - BE 70\% - DB 50\%}.
\item {\textbf{Project:} Auction System - \textbf{Contribute}: FE/BE/DB 35\%}. Study and support create, design and optimize service and Restful-API, tweak and optimize front-end.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Self Projects}
\begin{tightemize}
\item {\textbf{Detect 14 abnormal on lung}: Data source and information at Kaggle "vinbigdata-chest-xray-abnormalities-detection". This project apply GAN, DAE, etc. to dectect abnormal on lung. Handling data imbalance}
\item{\textbf{Detect fighting}: Apply 3DRestnet to feature extraction on video. Handling data imbalance and create demo.}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2020	     & Finalist & Lorem Ipsum\\
% 2018	     & $2^{nd}$ & Dolor Sit Amet\\
% 2015	     & Finalist  & Cras posuere\\
% \\
% \end{tabular}
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\sectionsep
C\# \textbullet{} Python \textbullet{} JavaScript \textbullet{}  SQL \textbullet{} CSS \textbullet{} HTML \textbullet{} DAX formula \textbullet{} Bash Script
\sectionsep
\subsection{Libraries/Frameworks Technical approach}
\sectionsep
ASP.NET \textbullet{MVC} \textbullet{Entity Framework} \textbullet{WPF} \textbullet{Swagger} \textbullet{CICD} \textbullet{jQuery} \textbullet{JSX syntax} \textbullet{Node.js} \textbullet{React} \textbullet{Jest} \textbullet{Kendo} \textbullet{Telerik} \textbullet{Bootstrap} \textbullet{Material UI} \textbullet{Redux} \textbullet{TensorFlow} \textbullet{PyTorch} \textbullet{Pandas} Pandas \textbullet{NumPy} \textbullet{Data Warehouse} \textbullet{Tabular model}
\sectionsep
\subsection{Tools/Platforms}
\sectionsep
Git \textbullet{VS Extension} \textbullet{VS TFVC} \textbullet{Visual Code} \textbullet{Visual Studio} \textbullet{Post Man}
\sectionsep
\subsection{Operating System}
Microsoft \textbullet{Linux}
\sectionsep
\subsection{Other Knowledges}
PCI \textbullet{Financial services} \textbullet{Scrum-Agile}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{UIT–VNU TP. Ho Chi
Minh}
\descript{Computer Science - Knowledge base and machine learning}
\location{2016-2019}
\vspace{0.5cm}
\textbullet{Attend att programming competition ACM – UIT}\\
\textbullet Top 4 of qualifying round Digital Race 2017 – 2018\\
\textbullet Application of Fuzzy Logic in control robot\\
\textbullet Knowledge Base Systems to solve math problems ( model
COKP, using Matlab).\\
\textbullet Generating Jazz automatically by genetic algorithms\\
\textbullet Part-of-Speech tagging for Vietnamese\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}

% \subsection{Graduate}
% Graduate Algorithms \textbullet{}\\ 
% Advanced Computer Architecture \textbullet{}\\ 
% Operating Systems \textbullet{}\\ 
% Artificial Intelligence \textbullet{}\\
% Visualization For Scientific Data \\
% \sectionsep

% \subsection{Undergraduate}

% Database Management Systems \textbullet{}\\
% Object Oriented Analysis and Design \textbullet{}\\
% Artificial Intelligence and Expert Systems \textbullet{}\\
% Scripting Languages and Web Tech \textbullet{}\\
% Software Engineering \\

\end{minipage} 
\end{document}  \documentclass[]{article}

